Paper Title

### 2023-01-16 paper.tex
Upload TeX file as an example
Add template for paper and appendix

\documentclass[letterpaper,12pt,leqno]{article}
\usepackage{paper,math}
\pdfoutput=1
\newcommand{\bib}{paper.bib}
\newcommand{\pdf}{figures.pdf}
\available{https://www.pascalmichaillat.org/13.html}
\hypersetup{pdftitle={u*=√uv}}

@@

\title{$\bm{u^*=\sqrt{uv}}$}
\author{Pascal Michaillat, Emmanuel Saez
\thanks{Pascal Michaillat: Brown University. Emmanuel Saez: University of California--Berkeley. We thank David Baqaee, Daniel Bogart, Varanya Chaubey, Olivia Lattus, Romain Ranciere, Guillaume Rocheteau, and Pierre-Olivier Weill for helpful comments and discussions.}}
\date{June 2022}

@@

Most governments are mandated to maintain their economies at full employment. We propose that the best marker of full employment is the efficient unemployment rate, $u^*$. We define $u^*$ as the unemployment rate that minimizes the nonproductive use of labor---both jobseeking and recruiting. The nonproductive use of labor is well measured by the number of jobseekers and vacancies, $u + v$. Through the Beveridge curve, the number of vacancies is inversely related to the number of jobseekers. With such symmetry, the labor market is efficient when there are as many jobseekers as vacancies ($u = v$), too tight when there are more vacancies than jobseekers ($v > u$), and too slack when there are more jobseekers than vacancies ($u > v$). Accordingly, the efficient unemployment rate is the geometric average of the unemployment and vacancy rates: $u^* = \sqrt{uv}$. We compute $u^*$ for the United States between 1930 and 2022. We find for instance that the US labor market has been over full employment ($u < u^*$) since May 2021.

\end{titlepage}\section{Introduction}

\paragraph{Full-employment mandate} Policymakers in many countries are mandated to maintain the economy at full employment. In the United States this legislative mandate comes from the 1978 Full Employment and Balanced Growth Act---itself an amendment of the 1946 Employment Act.\footnote{See \url{https://perma.cc/N4N5-BGJD} and \url{https://perma.cc/QK6U-C73K} for the history of these laws.} Despite the long existence of the full-employment mandate, there are no employment or unemployment rates that governments can use to capture full employment. In this paper, we produce an unemployment rate $u^*$ that characterizes a state of full employment.

\paragraph{Full employment does not mean no unemployment} Reaching full employment should be interpreted not as reaching zero unemployment. This is because it is not physically possible to reduce unemployment to zero. For instance, during World War 2, \citet[p. 125]{B44} noted that ``Even under full employment, there will be some unemployment \dots as there is some unemployment even in Britain at war to-day.''

\paragraph{So what is full employment} Rather, reaching full employment should be interpreted as reaching a socially desirable amount of unemployment. We define the socially efficient amount of unemployment as the amount that minimizes the nonproductive use of labor---both recruiting and jobseeking. It is because people constantly move in and out of jobs that unemployment cannot be reduced to zero, as noted by \citet[p. 125]{B44}: ``However great the unsatisfied demand for labor, there is an irreducible minimum of unemployment, a margin in the labor force required to make change and movement possible.'' Hence, while labor market flows are inevitable, the goal is that workers spend as much time as possible producing useful things and waste as little time as possible searching for employees or jobs.

\paragraph{Measuring jobseeking activity} The number of jobseekers is well measured by the number of unemployed workers. In theory, unemployed workers might also produce useful things at home beside looking for jobs. But in practice home production is minimal, so we count unemployed workers full-time jobseekers \citep[pp. 9--11]{MS16}.

\paragraph{Measuring recruiting activity} The number of recruiters is well measured by the number of vacancies. Indeed, it takes about one full-time worker to service a vacancy, so there are as many recruiters as vacancies \citep[p. 11]{MS16}.

\paragraph{Social objective} The social objective is to minimize the time spent on jobseeking and recruiting at the expense of producing. The amount of jobseeking is well measured by the number of unemployed workers, and the amount of recruiting by the number of job vacancies. Hence, the objective is to minimize the sum of the unemployment and vacancy rates, $u + v$.

\paragraph{Beveridge curve} Because of the Beveridge curve, it is not possible to reduce the numbers of jobseekers and vacancies at the same time. When the economy is depressed, there are many jobseekers and few vacancies; conversely, when the economy is booming, there are few jobseekers and many vacancies. The Beveridge curve is approximately a rectangular hyperbola:  $vu = A$, where $A$ is a constant \citep[figure 6]{MS16}. Hence, unemployment rate $u$ and vacancy rate $v$ are inversely related.

\paragraph{Efficiency criterion} Because of the symmetrical roles played by unemployed workers and vacant jobs, we find that the nonproductive use of labor is minimized when there are as many unemployed workers as vacant jobs ($u = v$). The labor market is inefficiently tight when there are more vacancies than jobseekers ($v > u$), and inefficiently slack when there are more jobseekers than vacancies ($u > v$).

\paragraph{Efficient labor-market tightness} The efficiency criterion can be reformulated in terms of labor-market tightness. The labor-market tightness is the ratio of vacancies to unemployment, $\t = v/u$. It measures the number of vacancies per unemployed worker. Our analysis implies that the efficient labor-market tightness is $\t^* = 1$. The labor market is inefficiently tight when $\t > 1$ and inefficiently slack when $\t < 1$.

\paragraph{Efficient unemployment rate} Because the unemployment and vacancy rates play a symmetric role on the labor market, the efficient unemployment rate is the geometric average of the unemployment and vacancy rates: $u^* = \sqrt{uv}$. This formula arises by combining the Beveridge curve, $uv = A$, and the result that the efficient unemployment and vacancy rates are equal.

\paragraph{Measuring the efficient unemployment rate the United States} Because it only requires unemployment and vacancy rates, the formula $u^* = \sqrt{uv}$ is easy to apply. In the United States, we can combine the historical unemployment and vacancy series produced by \citet{B10d} and \citet{PZ21} with the data produced by the Bureau of Labor Statistics to assemble monthly unemployment and vacancy series from 1930 and 2022. We use these series to compute the efficient unemployment rate $u^*$ between 1930 and 2022. We find that $u^*$ averages $4.2\%$ over the period and is very stable.

\paragraph{Application to the post-pandemic labor market} We also apply our formula in the post-pandemic period in the United States. There has been more vacant jobs than unemployed workers since May 2021, so the labor market has been too tight since then. In March 2022, there is twice as many vacant jobs as unemployed workers. Looking at historical data going back to 1930, we see that the last time that the labor-market tightness was so high, and the last time that the unemployment rate was so much below its efficient level, was at the end of World War 2. The post-pandemic labor market is in a very unusual situation: by any measure, 2022 is experiencing the tightest labor market since World War 2.

\paragraph{Application to modern monetary policy} During a press conference in May 2022, Jerome Powell, the chair of the Federal Reserve, discussed labor-market tightness at length.\footnote{See pp. 12--13 at \url{https://perma.cc/4EGU-XZYG}.} In response to a question from journalist Howard Schneider asking which tightness the Fed might target, he responded: ``So in terms of the vacancy-to-unemployment ratio, we don't have a goal in mind. There's no specific number that we're saying, `We've got to get to that.'  \dots I think when we got to one-to-one in the, you know, in the late teens, we thought that was a pretty good number. But, again, we're not shooting for any particular number.'' We find that a vacancy-to-unemployment ratio of $1$ is indeed what the Fed should target.

\section{Derivation of the efficient-unemployment formula}\label{s:formula}

This section derives the formula for the efficient unemployment rate: $u^* = \sqrt{uv}$.

\subsection{Definition of efficiency}

From a social perspective, it is optimal to maximize the number of people who spend time producing useful things rather than shuffling employees or jobs. This perspective is consistent with the view expressed by \citet[p. 20]{B44} that ``The material end of all human activity is consumption. Employment is wanted as a means to more consumption \dots as a means to a higher standard of life.'' We therefore define the socially efficient amount of unemployment as the amount that minimizes the nonproductive use of labor---both jobseeking and recruiting. Because people constantly move in and out of jobs, it is impossible to have zero unemployment, and it is impossible to have all workers devoted to production. While labor market flows are inevitable, the goal is that workers waste as little time as possible searching for jobs or employees.

\subsection{Measuring jobseeking activity}

The number of jobseekers is well measured by the number of unemployed workers. In theory, beside looking for jobs, unemployed workers might also produce useful things at home. Such home production would be included into aggregate production and contribute to social welfare. But in practice home production is minimal, as was already noted by \citet[p. 11]{R49}: ``The most important aspect of unemployment is its wastefulness. It is the existence of unused productive resources side by side with unsatisfied human needs that is the intolerable condition.'' \citet[pp. 9--11]{MS16} measure the fraction of nonwork time devoted to home production in the United States. The measure is based on the results by \citet{BM15}. Using administrative data from the US military, \citeauthor{BM15} study how servicemembers choose between reenlisting and leaving the military. The choices allow them to estimate the difference between market production and the sum of home production and public benefits during unemployment. Subtracting the value of public benefits from these estimates, \citet[p. 11]{MS16} find that the value of home production relative to market production could be as low as $0.03$. Given such low value, we assume that unemployed workers do not engage in home production at all, and we count them as full-time jobseekers.

\subsection{Measuring recruiting activity}

The number of recruiters is well measured by the number of vacancies. In theory it might take more or less than one full-time worker to service a vacancy. But in practice it takes about one full-time worker to service a vacancy, so the numbers of recruiters and vacancies are about the same. In the United States, the amount of labor required to service a vacancy can be measured from the National Employer Survey, which was conducted by the Census Bureau in 1997 \citep{V10}. \citet[p. 11]{MS16} estimate that servicing a vacancy requires $0.92$ worker at any point in time. So it takes about $1$ worker to service a vacancy, which is what we assume here by equating the number of recruiters to the number of vacancies.

\subsection{Shape of the Beveridge curve}

\paragraph{First observations of the Beveridge curve} Looking at labor-market statistics for the United Kingdom, \citet{B44} first noted that the number of vacancies and the number of jobseekers move in opposite directions. When the economy is in a slump, there are lots of jobseekers and few vacancies. Conversely, when the economy is in a boom, there are few jobseekers and many vacancies. This negative relationship between unemployment and vacancies---known as the Beveridge curve---was first plotted by \citet[figures 1 and 2]{DD58} using UK data for 1946--1956. Moreover, \citet[p. 22]{DD58} noted that the Beveridge curve looked like a rectangular hyperbola in an unemployment-vacancy plane.

\begin{figure}[t]
\subcaptionbox{Regular scale\label{f:regular1951}}{\includegraphics[scale=\sfig,page=1]{\pdf}}\hfill
\subcaptionbox{Log scale\label{f:log1951}}{\includegraphics[scale=\sfig,page=2]{\pdf}}
\caption{Unemployment and vacancy rates in the United States, 1951--2019}
\note{The unemployment rate is constructed by the \citet{UNRATE}. For 1951--2000, the vacancy rate is constructed by \citet{B10d}; for 2001--2019, the vacancy rate is the number of job openings divided by the civilian labor force, both measured by the \citet{CLF16OV,JTSJOL}. Unemployment and vacancy rates are quarterly averages of monthly series. The gray areas are NBER-dated recessions.}
\label{f:1951}\end{figure}

\paragraph{Unemployment and vacancy rates move in opposite directions} The Beveridge curve holds remarkably well in the United States as well \citep{BD89,EMR15}. Figure~\ref{f:regular1951} depicts the unemployment rate $u$ (all jobseekers divided by the labor force) and the vacancy rate $v$ (all vacancies divided by the same labor force) in the United States for 1951--2019. The unemployment rate is constructed by the \citet{UNRATE}. For 1951--2000, the vacancy rate is constructed by \citet{B10d}; for 2001--2019, the vacancy rate is the number of job openings divided by the civilian labor force, both measured by the \citet{CLF16OV,JTSJOL}. The figure shows clearly that unemployment and vacancy rates move in opposite directions.

\paragraph{Unemployment and vacancy rates are inversely related} In fact, unemployment and vacancy appear to be the inverse of each other, so that doubling the unemployment rate cuts the vacancy rate in half, and inversely, doubling the vacancy rate cuts the unemployment rate in half. Figure \ref{f:log1951} displays again unemployment and vacancy, but now in log scale. The fluctuations of the unemployment and vacancy rates are almost the mirror image of each other. This empirical regularity is particularly striking because the two series are constructed independently of each other.

\begin{figure}[p]
\subcaptionbox{1951Q1--1961Q1: elasticity $= -0.85$\label{f:branch1}}{\includegraphics[scale=\sfig,page=3]{\pdf}}\hfill
\subcaptionbox{1961Q2--1971Q4: elasticity $= -1.02$\label{f:branch2}}{\includegraphics[scale=\sfig,page=4]{\pdf}}\vfig
\subcaptionbox{1972Q1--1989Q1: elasticity $= -0.84$\label{f:branch3}}{\includegraphics[scale=\sfig,page=5]{\pdf}}\hfill
\subcaptionbox{1989Q2--1999Q2: elasticity $= -0.94$\label{f:branch4}}{\includegraphics[scale=\sfig,page=6]{\pdf}}\vfig
\subcaptionbox{1999Q3--2009Q3: elasticity $= -1.00$\label{f:branch5}}{\includegraphics[scale=\sfig,page=7]{\pdf}}\hfill
\subcaptionbox{2009Q4--2019Q4: elasticity $= -0.84$\label{f:branch6}}{\includegraphics[scale=\sfig,page=8]{\pdf}}
\caption{Estimated Beveridge curve in the United States, 1951--2019}
\note{This figure is constructed from figures 5 and 6 in \citet{MS16}. Unemployment and vacancy rates are the same as in figure~\ref{f:1951}. The number of structural breaks, dates of structural breaks, and elasticities of the Beveridge curve between breaks are estimated with the algorithm of \citet{BP98,BP03}.}
\label{f:hyperbola}\end{figure}

\paragraph{The Beveridge curve is a rectangular hyperbola} Mathematically, the property that unemployment and vacancy rates are inversely related implies that in an unemployment-vacancy plane, the Beveridge curve is a rectangular hyperbola:  
\begin{equation*}
vu = A,
\end{equation*}
where $A>0$ is a constant.

\paragraph{Estimates of the Beveridge elasticity} We can formally establish that the Beveridge curve is a rectangular hyperbola by estimating the elasticity of the vacancy rate with respect to the unemployment rate, $\odlx{v}{u}$. An elasticity of $-1$ corresponds to an hyperbola. \citet[figures 5 and 6]{MS16} use the algorithm of \citet{BP98,BP03} to estimate the structural breaks of the US Beveridge curve, and the elasticity of the Beveridge curve between these breaks. They find that the Beveridge elasticity remains between $-0.84$ and $-1.02$, so never far from $-1$ (figure~\ref{f:hyperbola}). This finding confirms that the Beveridge curve is close to an hyperbola.

\paragraph{Informal foundation for the hyperbolic Beveridge curve} Why is the Beveridge curve an hyperbola? Empirically, the number of new matches depends symmetrically on the number of jobseekers and vacancies. Doubling jobseekers increases new matches much the same as doubling vacancies. This makes sense as both jobseekers and vacancies are striving to find each other. This is obvious for jobseekers who spend time looking for jobs, applying, doing interviews. But this is also the case for vacancies as recruiters have to advertise vacancies, and screen and interview applicants. Therefore, as new matches have to meet the number of job separations, cutting in half the number of jobseekers requires doubling the number of vacancies, explaining why unemployment and vacancy rates are the inverse of each other.

\paragraph{Formal foundation for the hyperbolic Beveridge curve} In matching models the Beveridge curve says labor market flows are balanced: the number of job separations equals the number of jobs found. The employment rate $1-u$ is approximately constant around 1 since the unemployment rate $u$ is an order of magnitude less than 1. The job-separation rate $\l$ is also constant, so the number of job separations $\l (1-u)$ is approximately constant around $\l$. So at any point of the business cycle, the number of jobs found is approximately constant at $\l$.  With the standard symmetric Cobb-Douglas matching function, $m = \o \cdot\sqrt{uv}$, the number of jobs found at any point in time is proportional to $\sqrt{uv}$. \footnote{The US matching function appears to have a Cobb-Douglas form with exponents of $0.5$ on unemployment and vacancies. See \citet[p. 9]{MS16} for a survey of the US estimates based on aggregate data, and \citet{PP01} for a broader survey.} Hence $\sqrt{uv}$ is constant along the Beveridge curve, which implies $uv = \text{constant}$ along the Beveridge curve.

\subsection{Efficiency criterion}

The social objective is to minimize the time spent on jobseeking and recruiting at the expense of producing. Since the amount of jobseeking can be measured by the number of unemployed workers, and the amount of recruiting by the number of vacancies, the social objective is to minimize the sum of the unemployment and vacancy rates, $u + v$. This minimization is subject to the Beveridge curve constraint, $u v = \text{constant}$. Because of the Beveridge curve, it is not possible to reduce unemployment and vacancies at the same time. Therefore, the social planner must trade off unemployment and vacancies.

\paragraph{Symmetry argument} Because of the symmetrical roles played by unemployed workers and vacant jobs, the nonproductive use of labor is minimized when there are as many unemployed workers as vacant jobs ($u = v$). Indeed, we would like to minimize wasted resources from unemployment and from vacancies, subject to the Beveridge curve.  Since this problem is perfectly symmetric in $u$ and $v$, the solution to minimize waste is to have $u = v$.

\paragraph{Departure from efficiency} When the number of jobseekers is not equal to the number of vacancies, the labor market is operating inefficiently. The labor market is inefficiently tight when there are more vacancies than jobseekers ($v > u$). In that case, increasing $u$ and reducing $v$ would reduce waste. The labor market is inefficiently slack when there are more jobseekers than vacancies ($u > v$). Then, reducing $u$ and increasing $v$ would reduce waste.

\paragraph{First-order condition} We can also establish these results mathematically. The planner minimizes nonproduction $u + v$ subject to Beveridge curve $uv = A$, or $v = A/u$. This is equivalent to minimizing $u+A/u$, which is convex in $u$. A first-order condition is necessary and sufficient to find the minimum. We take the derivative of $u+A/u$ with respect to $u$ and set it to $0$. We obtain $1-A/u^2 = 0$. This condition implies that the minimum occurs when $u = \sqrt{A}$. By the Beveridge curve we have $v = A/u$, so at the minimum $v = A/ \sqrt{A} = \sqrt{A}$. Accordingly, the efficient unemployment and vacancy rates satisfy $u^* = v^* = \sqrt{A}$.

\paragraph{Formulation in terms of labor-market tightness} The efficiency criterion can be reformulated in terms of labor-market tightness. The labor-market tightness is the ratio of vacancies to unemployment, $\t = v/u$. It measures the number of vacancies per unemployed workers. The analysis implies that the efficient labor-market tightness is $\t^* = 1$; that the labor market is inefficiently tight when $\t > 1$; and that the labor market is inefficiently slack when $\t < 1$.

>>>>

\documentclass[letterpaper,12pt,leqno]{article}
\usepackage{paper}
\bibliographystyle{bibliography}
\hypersetup{pdftitle={Paper Title}}
% Enter permanent URL to paper
\available{https://github.com/pmichaillat/latex-paper}
% Enter BibTeX file with references here:
\newcommand{\bib}{bibliography.bib}
% Enter PDF file with figures here:
\newcommand{\pdf}{figures.pdf}

@@

\title{Paper Title}
\author{Author 1, Author 2
\thanks{Author 1: University 1. Author 2: University 2. We thank many colleagues for helpful comments and discussions. This work was supported by the a generous grant [grant number]; and another generous foundation.}}
\date{Month Year}

@@

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in culpa qui officia deserunt mollit anim id est laborum.

\end{titlepage}\section{Introduction}\label{s:introduction}

\paragraph{Research question} Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.\footnote{Excepteur sint, sunt in culpa qui officia deserunt mollit anim id est laborum.}

\paragraph{Positioning in the literature} Lorem ipsum dolor sit amet \citep{MS15}, consectetur adipiscing elit \citep[p. 1305]{MS19}, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua . \citet{M12,M14} enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.  Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur. \citeauthor{EMM21} aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.\footnote{In reprehenderit in eu fugiat nulla pariatur \citep{LMS18a}.}

\paragraph{Answer to the question} Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.\footnote{Sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident. Sunt in culpa qui officia deserunt mollit anim id est laborum. Excepteur sint occaecat cupidatat non proident.} Duis aute irure dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat nulla pariatur.

\paragraph{Another paragraph} Sed ut perspiciatis, unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam eaque ipsa, quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt, explicabo. Nemo enim ipsam voluptatem, quia voluptas sit, aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos, qui ratione voluptatem sequi nesciunt, neque porro quisquam est, qui dolorem ipsum, quia dolor sit amet consectetur adipiscing velit, sed quia non numquam eius modi tempora incidunt, ut labore et dolore magnam aliquam quaerat voluptatem.

\section{Section}\label{s:section}

Ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\subsection{A subsection with lists}\label{s:lists}

At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint.

Oobcaecati cupiditate non provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Here is a list:
\begin{itemize}
 	\item Et harum quidem rerum facilis est et expedita distinctio.
 	\item Nam libero tempore, cum soluta nobis est eligendi optio.
 	\item emporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet.
 		\begin{itemize}
 			\item cumque nihil impedit
 			\item quo minus id, quod maxime placeat
 			\item facere possimus, omnis voluptas assumenda est
 		\end{itemize}
\end{itemize}

Omnis dolor repellendus. And here is a numbered list:
\begin{enumerate}
 	\item Et harum quidem rerum facilis est et expedita distinctio.
 	\item Nam libero tempore, cum soluta nobis est eligendi optio.
 	\item emporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet.
	\begin{enumerate}
 			\item cumque nihil impedit
 			\item quo minus id, quod maxime placeat
 			\item facere possimus, omnis voluptas assumenda est
 	\end{enumerate}
\end{enumerate}
Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\subsection{Another subsection with text}

Sed ut perspiciatis, as showed in section \ref{s:lists}, unde omnis iste natus error sit voluptatem accusantium doloremque laudantium, totam rem aperiam eaque ipsa, quae ab illo inventore veritatis et quasi architecto beatae vitae dicta sunt, explicabo. Nemo enim ipsam voluptatem, quia voluptas sit, aspernatur aut odit aut fugit, sed quia consequuntur magni dolores eos, qui ratione voluptatem sequi nesciunt, neque porro quisquam est, qui dolorem ipsum, quia dolor sit amet consectetur adipiscing velit, sed quia non numquam eius modi tempora incidunt, ut labore et dolore magnam aliquam quaerat voluptatem. We will explore more in section \ref{s:graphs}.

\subsection{Some math and theorems}

\begin{proposition}\label{p:type1}  When the critical value is set to $z \in \mathbb{R}$, the probability of finding a type 1 error in a reported study is
\begin{equation}
S^*(z) = \frac{\bm{S(z)}}{ 1 -\zeta [1- \bm{S(z)}]}.
\label{e:type1}\end{equation}
The probability of type 1 error is larger when researchers p-hack ($S^*(z) > \bm{S(z)}$). In fact, the probability of type 1 error grows linearly with the expected number of p-hacking steps, which is givne by $\mathbb{E}(N(z))$:
\begin{equation}
S^*(z) = S(z) \times \mathbb{E}(N(z)).
\label{e:type1steps}\end{equation}
\end{proposition}

\begin{proof} There is a simple proof to this result. It is very simple. It is so simple. It gives equation \eqref{e:type1steps}.\end{proof}

 Quis autem vel eum iure reprehenderit, qui in ea voluptate velit esse, quam nihil molestiae consequatur $\bm{\alpha(X)}$ when researchers p-hack. Since the probability of type 1 error with p-hacking is given by \eqref{e:type1}, the robust critical value $z^*$ is implicitly defined by
\begin{equation*}
\frac{\mathcal{S}(z^*)}{1 -\theta + \theta \mathcal{S}(z^*)} = \sum_{\alpha=-\infty}^{+\infty}F^{\alpha} - \Lambda(\alpha).
\end{equation*}
From this implicit definition we obtain the following results (details of the proof are relegated to appendix~\ref{a:appendix1}):

\begin{lemma}\label{p:cv} For any hypothesis test with significance level $\alpha$, the robust critical value is
\begin{equation}
z^* = \int_{0}^{\infty} \alpha(i) \cdot \frac{1-\beta}{1-\alpha(i)\beta}\,di.
\label{e:cv}\end{equation}
The robust critical value is always larger than the classical critical value $\mathcal{Z}(\alpha)$. \end{lemma}

\paragraph{P-hacking under the robust critical value} Ut enim ad minima veniam, quis nostrum exercitationem ullam corporis suscipit laboriosam, nisi ut aliquid ex ea commodi consequatur? Combining equation \eqref{e:cv} with other results, we obtain the following corollary (the proof is in appendix~\ref{a:subappendix}):

\begin{corollary} The number of p-hacking steps under the robust critical value satisfies
\begin{equation*}
\mathbb{E}(N(z^*)) \approx \frac{1-\mathbb{P}(\alpha\pi)}{1-\pi}- \frac{f(y)}{z(p)^*} +P(\Gamma).
\end{equation*}\end{corollary}

\section{A section with graphs}\label{s:graphs}

Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat.

\subsection{A subsection with graphs}

At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\begin{figure}[t]
\subcaptionbox{First panel\label{f:panel1}}{\includegraphics[scale=\sfig,page=1]{\pdf}}\hfill
\subcaptionbox{Second panel\label{f:panel2}}{\includegraphics[scale=\sfig,page=2]{\pdf}}
\caption{A caption for the graph}
\note{A note for the graph. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus.}
\label{f:graph1}\end{figure}

\paragraph{Description of a result} Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Figure~\ref{f:graph1} depicts the result.

\paragraph{Another result in a panel} In fact, nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Figure \ref{f:panel1} displays again this fact, but now in log scale. This empirical regularity is particularly striking in figure \ref{f:panel2} because the two series are constructed independently of each other.

\subsection{A full-page graphs}

A full-page graph is on figure \ref{f:graph2}. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus.

\begin{figure}[p]
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=1]{\pdf}}\hfill
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=2]{\pdf}}\vfig
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=3]{\pdf}}\hfill
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=4]{\pdf}}\vfig
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=5]{\pdf}}\hfill
\subcaptionbox{Caption for panel}{\includegraphics[scale=\sfig,page=1]{\pdf}}
\caption{A caption for the graph}
\note{A note for the graph. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat. The figures are borrowed from \citet[section 3]{MS22b}.}
\label{f:graph2}\end{figure}

\paragraph{Informal description of the results} At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\paragraph{Formal description of the results} At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga. Et harum quidem rerum facilis est et expedita distinctio. Nam libero tempore, cum soluta nobis est eligendi optio, cumque nihil impedit, quo minus id, quod maxime placeat, facere possimus, omnis voluptas assumenda est, omnis dolor repellendus. Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\section{A section with table}

Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat.

\subsection{The table}

Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Itaque earum rerum hic tenetur a sapiente delectus, ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat. Table \ref{t:table} shows many things.

At vero eos et accusamus et iusto odio dignissimos ducimus, qui blanditiis praesentium voluptatum deleniti atque corrupti, quos dolores et quas molestias excepturi sint, obcaecati cupiditate non provident, similique sunt in culpa, qui officia deserunt mollitia animi, id est laborum et dolorum fuga.

\begin{table}[t]
\caption{A caption for the table}
\begin{tabular*}{\textwidth}[]{p{3.3cm}@{\extracolsep\fill}cccc}
\toprule
& Timeline & Natural rate & Monetary  & Government \\
&  & of interest &  policy & spending\\
\midrule
\multicolumn{5}{l}{A. ZLB episode}\\
ZLB: & $t\in (0,T) $ & $r^n<0$ & $i=0$  & -- \\
Normal times: & $t>T$ &  $r^n>0$ & $i= r^n + \phi \pi$  & --   \\
\midrule
\multicolumn{5}{l}{B. ZLB episode with forward guidance}\\
ZLB: & $t\in (0,T)$ & $r^n<0$ & $i=0$  & -- \\
Forward guidance: & $t\in (T,T+\Delta)$ & $r^n>0$ & $i=0$  & --\\
Normal times: & $t>T+\Delta$ & $r^n>0$ & $i= r^n + \phi \pi$  & -- \\
\midrule
\multicolumn{5}{l}{C. ZLB episode with government spending}\\
ZLB: & $t\in (0,T) $ & $r^n<0$ & $i=0$  & $g>0$  \\
Normal times: & $t>T$ & $r^n>0$ & $i= r^n + \phi \pi$  & $g=0$   \\
\bottomrule
\end{tabular*}
\note{This table describes three scenarios: Temporibus autem quibusdam et aut officiis debitis aut rerum necessitatibus saepe eveniet, ut et voluptates repudiandae sint et molestiae non recusandae. Ut aut reiciendis voluptatibus maiores alias consequatur aut perferendis doloribus asperiores repellat. The table is borrowed from \citet[table 1]{MS21a}.}
\label{t:table}\end{table}
